ACNP 2024 MS ANXIETY

### 2024-08-09 scripts/MSAnxiety_manuscript_audrey_replication.Rmd
Add files via upload

Final N demographics

(unique, with good MIMoSA):

### testing mean UF in depression group  - NS!!!
(previous script (~/BBL/msdepression/scripts/Biological_Psychiatry_Revision_Scripts/msdepression_n380_started_20230927_mm_BP_r1.Rmd)), lines 734 and  779-781
  #bilat: depGroupVar        85.32     206.70   t=0.413    p=0.680    
  disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ depGroupVar + osex+PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)
  summary(disease_mean_UF_vol_lm)
#findings

@@

#open Rds
data_2023_pull <- readRDS(paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rds"))
```

@@

#1 Total unique individuals who also have MS - 890
#2 Total unique who had good MIMoSA - 786
#3 Total unique with bad MIMoSA - 890-786 = 104
#4 Total lost in streamline filtering - 3
#5 Final N going into inclusion/exclusion - 783

#read in mimosa data
mimosa_qc <- read.csv("/Users/eballer/BBL/msdepression/data/melissa_martin_files/csv/mimosa_dataframe", sep = ",", header = FALSE) #n=2840

#preprocess data frame to extract dates, empis, and score
empis_with_qc <- mimosa_qc %>% 
  mutate(EMPI = as.factor(gsub(x = V5, pattern = ".*sub-(.*)/ses-.*/.*", replacement="\\1", perl = TRUE))) %>%
  mutate(EXAM_DATE = gsub(x=V5, pattern = ".*/ses-(.{8})/.*", replacement = "\\1\\2\\3")) %>% 
  mutate(score = V3)

#merge with whole data frame to make sure we exclude people w/out MS
mimosa_qc_df <- merge(data_2023_pull, empis_with_qc, by = c("EMPI", "EXAM_DATE")) #n = 3592

#get list of unique patients, n = 890
mimosa_qc_unique <- mimosa_qc_df %>%
  group_by(EMPI) %>%
  arrange(EXAM_DATE) %>%
  slice(1) %>%
  ungroup #n=890

@@

 #n = 812
df_demo_and_fascicles <- df_people_with_good_mimosa %>% 
  left_join(fascicle_proportions, by = c("EMPI", "EXAM_DATE")) %>%
  filter(!is.na(Has.MS.Provider)) %>% #remove people who don't have MS provider
  filter(!is.na(CNII_L)) #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs

@@

lesion_volumes <- read.csv("/Users/eballer/BBL/msdepression/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes", sep = ",", header = TRUE) #n=958 unique, identical to fascicle unique
lesion_volumes <- lesion_volumes %>%
  mutate(EMPI = as.character(EMPI)) %>%
  mutate(EXAM_DATE = as.character(EXAM_DATE))

@@

##YEO Networks
###Read in fascicle info
```{r read_in_yeo_fascicle_info}
##########################################################
#             Read in Fascicle info             #
##########################################################
########
#fascicle volumes in yeo networks
########

#read in file with proportions
#fascicle_volumes_yeo_7 <- read.csv(paste0(homedir, "results/yeo_7_network_overlap_proportions.txt"), header = T, sep = ",", na.strings="0")

#make titles nice
#names(fascicle_volumes_yeo_7) <-gsub("prop_in_mask_", "prop_", names(fascicle_volumes_yeo_7))

#make Nas into 0
#fascicle_volumes_yeo_7[is.na(fascicle_volumes_yeo_7)]=0

#read in file with binarized yes/no 
fascicle_volumes_yeo_7_binarized <- read.csv("/Users/eballer/BBL/msdepression/results/yeo_7_network_overlap_proportions_binarized.txt", header = T, sep = ",")

#drop cranial nerves
fascicle_volumes_yeo_7_binarized_no_cranial_nerves <- fascicle_volumes_yeo_7_binarized %>% filter(!grepl('CN', fascicle))

#check that order of df is same as yeo networks
new_df <- gsub(pattern = "_vol", replacement = "", x = names(df_demo_and_fascicles[grep(pattern = "_vol", x = names(df_demo_and_fascicles))]))

combined_df <- data.frame(cbind(new_df, fascicle_volumes_yeo_7_binarized_no_cranial_nerves$fascicle))
names(combined_df) <- c("df", "yeo")

#they match
combined_df$match <- combined_df$df == combined_df$yeo
```

### Calc healthy volume of yeo networks
```{r calc_healthy_volume_of_yeo_networks}
#multiply with the binary yeo maps to get absolute volumes of healthy
fascicle_volumes_yeo_7_full_volumes <- fascicle_volumes_yeo_7_binarized_no_cranial_nerves %>% 
  tibble::remove_rownames() %>%
  tibble::column_to_rownames(var = 'fascicle') %>%
  mutate(across(everything()) * fiber_volume_values_no_cranial_nerves$volume_full) %>%
  rename_with(~ str_c(.x, "_vol"), everything())

#sum the volumes of each network to get total. 
sums_of_volume_of_healthy_fascicles_by_network <- fascicle_volumes_yeo_7_full_volumes %>%
  summarise(across(everything(), ~ sum(., na.rm = TRUE)))

###Calculate injury to yeo networks for each subject
```{r calculate_injury_to_network}

#grab names of networks, get rid of first element which is "fasiscle"
yeo_network_names <- names(fascicle_volumes_yeo_7_binarized_no_cranial_nerves)[-1]

#make names with _prop_net for use later to grap columns of proportions and not volumes
yeo_network_names_prop <- paste(yeo_network_names, 'prop_net', sep = '_')

df_w_yeo_volume_info <- df_demo_and_fascicles %>%
  # mutate(total_fascicle_vol_lost = rowMeans(across(all_of(fascicle_names_w_vol_suffix)))) %>%
  dplyr::select(EMPI, ends_with("_vol")) %>%
  ungroup()

#add columns to data frame for each network
df_w_yeo_volume_info[,yeo_network_names] = 0

#this has been checked with eyeballs and works. You CAN trust the df_w_yeo_volume_info
for (network in yeo_network_names) {

  for (subj in 1:dim(df_w_yeo_volume_info)[1]) {
      # multiply the binary vector of the network with the fascicle volumes of injury, sum, and store in data frame
      text_to_eval <- paste0("df_w_yeo_volume_info$", network,"[", subj,"]=sum(fascicle_volumes_yeo_7_binarized_no_cranial_nerves$", network,
      "*df_w_yeo_volume_info[",subj,",3:(dim(df_w_yeo_volume_info)[2] - 7)])")
     # print(text_to_eval)
      eval(parse(text=text_to_eval))
  }
}

### going to add 7 more columns to the data frame that contain the volume of injury/total healthy volume
df_w_yeo_volume_info_with_prop_of_network <- tibble(df_w_yeo_volume_info) %>% 
  mutate(across(all_of(yeo_network_names), 
    .names = "{.col}_prop_net"

  ))

#go through each subject, and divide their total volume of injury within each network by the overall volume of the network
for (subj in 1:dim(df_w_yeo_volume_info_with_prop_of_network)[1]){
  df_w_yeo_volume_info_with_prop_of_network[subj, grepl(x = names(df_w_yeo_volume_info_with_prop_of_network), pattern = "_prop_net")] = df_w_yeo_volume_info_with_prop_of_network[subj, grepl(x = names(df_w_yeo_volume_info_with_prop_of_network), pattern = "_prop_net")]/sums_of_volume_of_healthy_fascicles_by_network
}

### rename the whole new data frame df_demo_and_fascicles
df_demo_and_fascicles <- df_w_yeo_volume_info_with_prop_of_network %>% 
  dplyr::select(-contains('_vol')) %>% #removes all columns with volume, leaving only the exam date, empi, and yeo values
  right_join(df_demo_and_fascicles, by = c("EXAM_DATE", "EMPI")) #combine with demo_and_fascicles

```
##Anxiety Network from neurosynth (association, not uniformity)
###read in file with fasciclexanxiety overlap, and define anxiety network
```{r read_in_neurosynth_anxiety_network}
neurosynth_anxiety_network_fascicle_overlap <- read.csv("/Users/eballer/BBL/msanxiety/results/streamline_volume_within_anxiety_network_association_neuro_maps_FDR_01.csv", header = T, sep = ",") %>% 
  filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves))) %>% #get rid of cranial nerves up front 
  replace(is.na(.), 0)

fascicles_with_any_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
  filter(prop_in_mask > 0)  #n = 43

#top 25% 
#number_of_brain_regions_in_top_25 <- round((dim(fascicles_with_any_anxiety_overlap)[1]/4)) #n=11
number_of_brain_regions_in_top_25 <- round((dim(neurosynth_anxiety_network_fascicle_overlap)[1]/4)) #n=19

fascicles_with_vol_top_25_percent_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
  filter(!is.na(prop_in_mask)) %>%
  arrange(desc(non_zero_voxels_in_anxiety_map)) %>%
  slice(1:number_of_brain_regions_in_top_25)

fascicles_with_prop_top_25_percent_anxiety_overlap <- neurosynth_anxiety_network_fascicle_overlap %>%
  filter(!is.na(prop_in_mask)) %>%
  arrange(desc(prop_in_mask)) %>%
  slice(1:number_of_brain_regions_in_top_25)

#name vectors to use later
fascicle_names_any_anxiety_overlap_vol <- fascicles_with_any_anxiety_overlap$fascicle 
fascicle_names_top_25_vol <- fascicles_with_vol_top_25_percent_anxiety_overlap$fascicle 
fascicle_names_bottom_75_vol <- neurosynth_anxiety_network_fascicle_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_vol)) %>% pull(fascicle)

fascicle_names_any_anxiety_overlap_prop <- fascicles_with_any_anxiety_overlap$fascicle
fascicle_names_top_25_prop <-fascicles_with_prop_top_25_percent_anxiety_overlap$fascicle 
fascicle_names_bottom_75_prop <- neurosynth_anxiety_network_fascicle_overlap %>% filter(!(fascicle %in% fascicle_names_top_25_prop)) %>% pull(fascicle)

##add vol/prop
fascicle_names_any_anxiety_overlap_vol_w_suff <- fascicle_names_any_anxiety_overlap_vol %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
fascicle_names_top_25_vol_w_suff <- fascicle_names_top_25_vol %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)
fascicle_names_bottom_75_vol_w_suff <- fascicle_names_bottom_75_vol  %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in

fascicle_names_any_anxiety_overlap_prop_w_suff <- fascicle_names_any_anxiety_overlap_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
fascicle_names_top_25_prop_w_suff <- fascicle_names_top_25_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
fascicle_names_bottom_75_prop_w_suff <- fascicle_names_bottom_75_prop %>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)

# Total volume of injury within each anxiety network, double checked that : top_25_total_volume + bottom_75_total_volume
total_fascicle_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total)
any_anxiety_overlap_total_volume <- sum(fascicles_with_any_anxiety_overlap$num_voxels_total) # vol = 1093606
top_25_total_volume <-sum(fascicles_with_vol_top_25_percent_anxiety_overlap$num_voxels_total) # vol = 548305
bottom_75_total_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total[neurosynth_anxiety_network_fascicle_overlap$fascicle %in% fascicle_names_bottom_75_vol]) #vol = 548305

### Sort all the fascicles by %overlap, in decreasing order (so highest overlap at the top), and then take names of the top quartile, save for making binary maps later
anxiety_network_names_top_quartile_no_cranial_nerves<- (neurosynth_anxiety_network_fascicle_overlap[order(neurosynth_anxiety_network_fascicle_overlap$non_zero_voxels_in_anxiety_map, decreasing = TRUE),])$fascicle[1:number_of_brain_regions_in_top_25]

write.table(anxiety_network_names_top_quartile_no_cranial_nerves, paste0(homedir, "/results/anxiety_network_names_top_quartile_no_cranial_nerves_by_vol.txt"), row.names = F, col.names = F, quote = F)

df_for_making_binary_color_maps_vol <- neurosynth_anxiety_network_fascicle_overlap %>% dplyr::select(fascicle, non_zero_voxels_in_anxiety_map)

write.table(df_for_making_binary_color_maps_vol, paste0(homedir, "/results/volume_of_overlap_w_anxiety_net_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")

df_for_making_binary_color_maps_prop <- neurosynth_anxiety_network_fascicle_overlap %>% dplyr::select(fascicle, prop_in_mask)

write.table(df_for_making_binary_color_maps_prop, paste0(homedir, "/results/proportion_of_overlap_w_anxiety_net_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")

### Get dep network data
```{r depression_network_injury}
#take depression network from the BP paper, and find names of fascicles in each group

#read in depression network overlap by volume data frame
dep_net_overlap_from_bp_paper <- read.csv("/Users/eballer/BBL/msdepression/results/df_fascicles_sorted_by_volume_in_mask_for_eTable3.csv", sep = ",", header = TRUE)

dep_net_top_25_percent <- dep_net_overlap_from_bp_paper$fascicle[1:round((dim(dep_net_overlap_from_bp_paper)[1]/4),0)]
dep_net_top_25_percent_w_suff <- dep_net_top_25_percent %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)

top_25_total_volume_dep <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[1:round((dim(dep_net_overlap_from_bp_paper)[1]/4),0)])

nondep_net_bottom_75_percent <- dep_net_overlap_from_bp_paper$fascicle[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]]
nondep_net_bottom_75_percent_w_suff <- nondep_net_bottom_75_percent %>%gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)

bottom_75_total_volume_nondep <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[(round(dim(dep_net_overlap_from_bp_paper)[1]/4,0) +1):dim(dep_net_overlap_from_bp_paper)[1]])

### find names of fascicles in anxiety + dep network, unique to dep net, and unique to anxiety net
```{r find_names_and_overlaps_of_dep_and_anxiety_networks}

#I want to figure out what the volume is in all voxels within the overlap of depression and anxiety network, as well as within the nonoverlapping networks
#the depression net overlap from bp paper contains a colum (num_voxels_total) that has the full voxel sizes of all of the fascicles. Will use this to help find the "total volume size"

#total volume = 1545449
#checked to make sure that dep_only_net_vol + anxiety_only_net_vol + dep_and_anxiety_net_overlap_net_volume = dep_and_anxiety_net_unique_net_volume

dep_and_anxiety_combined <- c(fascicle_names_top_25_vol, dep_net_top_25_percent) #n = 38

dep_and_anxiety_net_unique_names <- dep_and_anxiety_combined %>% unique() #n=34
dep_and_anxiety_net_unique_net_volume <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_unique_names]) #vol = 1048643

dep_and_anxiety_net_overlap_names <- dep_and_anxiety_combined[dep_and_anxiety_combined %>% duplicated()] #n=4
dep_and_anxiety_net_overlap_net_volume <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_overlap_names]) #vol = 486260

dep_and_anxiety_net_overlap_names_no_CC <- dep_and_anxiety_net_overlap_names[dep_and_anxiety_net_overlap_names != "CC"]
dep_and_anxiety_net_overlap_net_volume_no_CC <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_overlap_names_no_CC]) #vol = 95659

dep_only_names <- dep_and_anxiety_net_unique_names[!(dep_and_anxiety_net_unique_names %in% fascicle_names_top_25_vol)] #n=15
dep_only_net_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_only_names]) #vol = 370747

anxiety_only_names <-dep_and_anxiety_net_unique_names[!(dep_and_anxiety_net_unique_names %in% dep_net_top_25_percent)] #n=15
anxiety_only_net_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% anxiety_only_names]) #vol = 191636

### add suffix
dep_and_anxiety_net_unique_names_w_suff <- dep_and_anxiety_net_unique_names  %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in

dep_and_anxiety_net_overlap_names_w_suff <- dep_and_anxiety_net_overlap_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in

dep_and_anxiety_net_overlap_names_w_suff_no_CC <- dep_and_anxiety_net_overlap_names_no_CC %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in

dep_only_names_w_suff <- dep_only_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in

anxiety_only_names_w_suff <- anxiety_only_names %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in 
```

### Define anxiety net by top 25 in both vol/prop
```{r defineanxietynet_with_25_propx25vol}
##### make an array of fascicles that have both substantial overlap with the anxiety network (top 25% vol), and where each fascicle is substantially impacted (top 25% proportion), n = 14
fascicle_names_top_25_vol_x_top_25_prop <- fascicle_names_top_25_vol[fascicle_names_top_25_vol %in% fascicle_names_top_25_prop]

#add vol/prop suffixes
fascicle_names_top_25_vol_x_top_25_prop_PROP_suffix <-fascicle_names_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
fascicle_names_top_25_vol_x_top_25_prop_VOL_suffix <-fascicle_names_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)

#create fascicle vectors that don't include these special fascicles, n = 63
fascicle_names_NOT_top_25_vol_x_top_25_prop <- fascicle_names_no_cranial_nerves[!(fascicle_names_no_cranial_nerves %in% fascicle_names_top_25_vol_x_top_25_prop)]

#add vol/prop suffixes
fascicle_names_NOT_top_25_vol_x_top_25_prop_PROP_suffix <- fascicle_names_NOT_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_prop", perl=TRUE)
fascicle_names_NOT_top_25_vol_x_top_25_prop_VOL_suffix <- fascicle_names_NOT_top_25_vol_x_top_25_prop%>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE)

#anxiety25_propxvol overlap total, sum of these two is 1545449 (and this is total_fascicle_volume)
anxiety_top_25_vol_x_top_25_prop_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% fascicle_names_top_25_vol_x_top_25_prop]) #vol = 181869

#nonanxiety25_propxvol overlap total
anxiety_NOT_top_25_vol_x_top_25_prop_vol <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% fascicle_names_NOT_top_25_vol_x_top_25_prop]) #vol = 1363580

#check sums
if ((anxiety_top_25_vol_x_top_25_prop_vol + anxiety_NOT_top_25_vol_x_top_25_prop_vol) == total_fascicle_volume) {
  print("anxiety + nonanxiety net = total fascicle volume")
} else{
  print("something is wrong with counts")
}

@@

  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) 
  mutate(sum_fascicle_vol_lost_inanxietynet_all = 
           rowSums(across(all_of(fascicle_names_any_anxiety_overlap_vol_w_suff)))) %>%
  mutate(proportion_volume_lost_anxiety_net_by_network_size_sum = sum_fascicle_vol_lost_inanxietynet_all/any_anxiety_overlap_total_volume) %>%

  #sum of total volume lost in anxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) top quartile
  mutate(sum_fascicle_vol_lost_inanxietynet_top_quartile = 
           rowSums(across(all_of(fascicle_names_top_25_vol_w_suff)))) %>%
  mutate(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 = sum_fascicle_vol_lost_inanxietynet_top_quartile/top_25_total_volume) %>%

  #sum of total volume lost in nonanxiety network and proportion of volume lost in anxiety network (volume lost/network volume size) bottom 3 quartiles
  mutate(sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles = 
           rowSums(across(all_of(fascicle_names_bottom_75_vol_w_suff)))) %>%
  mutate(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 = sum_fascicle_vol_lost_nonanxiety_net_bottom_3_quartiles/bottom_75_total_volume) %>%

  ##sum of total volume lost in depression network and proportion of volume lost in depression network (volume lost/network volume size) top quartile
  mutate(sum_fascicle_vol_lost_indepressionnet_top_quartile = 
           rowSums(across(all_of(dep_net_top_25_percent_w_suff)))) %>%
  mutate(proportion_volume_lost_depression_net_by_network_size_sum_top_25 = sum_fascicle_vol_lost_indepressionnet_top_quartile/top_25_total_volume_dep) %>%

  #sum of total volume lost in nondepression network and proportion of volume lost in depression network (volume lost/network volume size) bottom 3 quartiles
  mutate(sum_fascicle_vol_lost_nondepression_net_bottom_3_quartiles = 
           rowSums(across(all_of(nondep_net_bottom_75_percent_w_suff)))) %>%
  mutate(proportion_volume_lost_nondepression_net_by_network_size_sum_bottom_75 = sum_fascicle_vol_lost_nondepression_net_bottom_3_quartiles/bottom_75_total_volume_nondep) %>%

  ##sum of total volume lost in depression + anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_combined = 
           rowSums(across(all_of(dep_and_anxiety_net_unique_names_w_suff)))) %>%
  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_combined = sum_fascicle_vol_lost_indep_and_anxiety_net_combined/dep_and_anxiety_net_unique_net_volume) %>%

  ##sum of total volume lost in areas of overlap between depression + anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_overlap = 
           rowSums(across(all_of(dep_and_anxiety_net_overlap_names_w_suff)))) %>%
  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap = sum_fascicle_vol_lost_indep_and_anxiety_net_overlap/dep_and_anxiety_net_overlap_net_volume) %>%

  ##sum of total volume lost in areas of overlap between depression + anxiety network and proportion of volume lost in network (volume lost/network volume size), no CC
  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = 
           rowSums(across(all_of(dep_and_anxiety_net_overlap_names_w_suff_no_CC)))) %>%
  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC/dep_and_anxiety_net_overlap_net_volume_no_CC) %>%

  ##sum of total volume lost in depression, no overlap with anxiety network and proportion of volume lost in network (volume lost/network volume size) top quartile
  mutate(sum_fascicle_vol_lost_indepressionnet_no_anxiety_overlap = 
           rowSums(across(all_of(dep_only_names_w_suff)))) %>%
  mutate(proportion_fascicle_vol_lost_indepressionnet_no_anxiety_overlap = sum_fascicle_vol_lost_indepressionnet_no_anxiety_overlap/dep_only_net_vol) %>%

    ##sum of total volume lost in anxiety, no depression overlap network and proportion of volume lost in network (volume lost/network volume size) top quartile
  mutate(sum_fascicle_vol_lost_inanxietynet_no_depression_overlap = 
           rowSums(across(all_of(anxiety_only_names_w_suff)))) %>%
  mutate(proportion_fascicle_vol_lost_inanxietynet_no_depression_overlap = sum_fascicle_vol_lost_inanxietynet_no_depression_overlap/anxiety_only_net_vol) %>%

    ##sum of total volume lost in anxiety 25 volxanxiety25prop groups, and proportion of volume lost in network (volume lost/network volume size)
  mutate(sum_fascicle_names_top_25_vol_x_top_25_prop = 
           rowSums(across(all_of(fascicle_names_top_25_vol_x_top_25_prop_VOL_suffix)))) %>%
  mutate(proportion_fascicle_vol_lost_top_25_vol_x_top_25_prop = sum_fascicle_names_top_25_vol_x_top_25_prop/anxiety_top_25_vol_x_top_25_prop_vol) %>%

    ##sum of total volume lost in remaining 63 fascicles NOT in anxiety 25 volxanxiety25prop groups, and proportion of volume lost in network (volume lost/network volume size)
  mutate(sum_fascicle_names_NOT_top_25_vol_x_top_25_prop = 
           rowSums(across(all_of(fascicle_names_NOT_top_25_vol_x_top_25_prop_VOL_suffix)))) %>%
  mutate(proportion_fascicle_vol_lost_NOT_top_25_vol_x_top_25_prop = sum_fascicle_names_NOT_top_25_vol_x_top_25_prop/anxiety_NOT_top_25_vol_x_top_25_prop_vol) %>%

   ##mean_uncinate)
  mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
  mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2) %>%

@@

df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)

 tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

>>>>

Groups:
1. Total unique individuals who also have MS - 1026
2. Total unique who had good MIMoSA - 867 (lost 159)
3. Remove people without MS provider, n=823 (lost 44)
4. Remove people with bad streamline filtering, n=854 (lost 13)
5. Remove people without MS provider, n=812 (lost 42)

### testing mean UF in depression group  - NS!!!
(previous script (~/BBL/msdepression/scripts/Biological_Psychiatry_Revision_Scripts/msdepression_n380_started_20230927_mm_BP_r1.Rmd)), lines 734 and  779-781
  #bilat: depGroupVar        85.32     206.70   t=0.413    p=0.680    
  disease_mean_UF_vol_lm <- lm(mean_UF_vol ~ depGroupVar + osex+PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)
  summary(disease_mean_UF_vol_lm)

@@

#open Rds, n=51238
data_2023_pull <- readRDS(paste0(homedir, "/data/data_2023_pull_with_curated_icd10_codes.rds"))
```

@@

#read in mimosa data
mimosa_qc <- read.csv("/Users/eballer/BBL/msdepression/data/melissa_martin_files/csv/mimosa_dataframe", sep = ",", header = FALSE) #n=2841

#preprocess data frame to extract dates, empis, and score, n=2841
empis_with_qc <- mimosa_qc %>% 
  mutate(EMPI = as.factor(gsub(x = V5, pattern = ".*sub-(.*)/ses-.*/.*", replacement="\\1", perl = TRUE))) %>%
  mutate(EXAM_DATE = gsub(x=V5, pattern = ".*/ses-(.{8})/.*", replacement = "\\1\\2\\3")) %>% 
  mutate(score = V3)

#merge with whole data frame to make sure we exclude people w/out MS
mimosa_qc_df <- merge(data_2023_pull, empis_with_qc, by = c("EMPI", "EXAM_DATE")) #n = 11252

#get list of unique patients, n = 1026
mimosa_qc_unique <- mimosa_qc_df %>%
  group_by(EMPI) %>%
  arrange(EXAM_DATE) %>%
  slice(1) %>%
  ungroup

@@

 #n = 812
df_demo_and_fascicles <- df_people_with_good_mimosa %>% 
  left_join(fascicle_proportions, by = c("EMPI", "EXAM_DATE")) %>%
  filter(!is.na(CNII_L)) %>% #this is a sample fascicle that should have a value. if it does not, it means something is usually wrong with whole person. Remove rows with NAs, n=854, lost 13
  filter(!is.na(Has.MS.Provider))  #remove people who don't have MS provider, n=823 (lost 42)

@@

lesion_volumes <- read.csv("/Users/eballer/BBL/msdepression/results/mimosa_binary_masks_hcp_space_20211026_n2336_volumes", sep = ",", header = TRUE) #n=2336, 958 unique, identical to fascicle unique
lesion_volumes <- lesion_volumes %>%
  mutate(EMPI = as.character(EMPI)) %>%
  mutate(EXAM_DATE = as.character(EXAM_DATE))

@@

##Anxiety Network from neurosynth (association, not uniformity)
###read in file with fasciclexanxiety overlap, and define anxiety network
```{r read_in_neurosynth_anxiety_network}
neurosynth_anxiety_network_fascicle_overlap <- read.csv("/Users/eballer/BBL/msanxiety/results/streamline_volume_within_anxiety_network_association_neuro_maps_FDR_01.csv", header = T, sep = ",") %>% 
  filter(fascicle %in% fascicle_names_no_cranial_nerves) %>%
  slice(order(factor(fascicle, levels = fascicle_names_no_cranial_nerves))) %>% #get rid of cranial nerves up front 
  replace(is.na(.), 0)

# Total volume of healthy fascicles within brain
total_fascicle_volume <- sum(neurosynth_anxiety_network_fascicle_overlap$num_voxels_total)

@@

  ##mean_uncinate
  mutate(mean_UF_vol = (UF_L_vol + UF_R_vol)/2) %>%
  mutate(mean_UF_prop = (UF_L_prop + UF_R_prop)/2) %>%

  ##mean_fornix
  mutate(mean_fornix_volume = (F_L_vol + F_R_vol)/2) %>%
  mutate(mean_fornix_prop = (F_L_prop + F_R_prop)/2) %>%

@@

df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>% 
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, UF_L_prop, UF_R_prop, oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex)

 tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Female") %>%
  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_females

    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Male") %>%
  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_males
